Local PCA results

### 2017-01-12 medicago/medicago_data_setup.Rmd
renamed package/ directory lostruct/ and changed load_all to library()

```{r setup}
devtools::load_all("../package")
library(Matrix)
library(colorspace)
options(width=100)
fig.dim <- 4
knitr::opts_chunk$set(fig.width=2*fig.dim,fig.height=fig.dim,fig.align='center')
```

>>>>

```{r setup}
library(lostruct)
library(Matrix)
library(colorspace)
options(width=100)
fig.dim <- 4
knitr::opts_chunk$set(fig.width=2*fig.dim,fig.height=fig.dim,fig.align='center')
```
